\documentclass[11pt]{article}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}

\begin{document}
\title{MAT1830 --- Assignment 7}
\author{Dylan Pinn --- 24160547}
\maketitle

\section*{Question 1}

Let $R$ be the relation on $\mathbb{Z} \times \mathbb{Z}$ defined by $(w, x)R(y,
z)$ if any only if $w + x \leq y + z$.

Let $S$ be the relation on $\mathbb{Z} \times \mathbb{Z}$ defined by $(w, x)S(y,
z)$ if and only if $w \leq y$ and $x \leq z$

\begin{enumerate}[label= (\alph*)]
  \item Is $R$ antisymmetric?

  \item Is $S$ antisymmetric?
\end{enumerate}

\section*{Question 2}

You know the following facts about a relation $T$:

\begin{itemize}
  \item $T$ is defined on the set $\{a, b, c, d, e \}$,
  \item $aTc, bTc, cTd, eTb$ and $e\not{T}a$,
  \item $T$ is a particular order relation.
\end{itemize}

Draw a Hasse diagram for every possible relation that $T$ could be and, for
each, write down whether it is a total order relation.

\section*{Question 3}

Find expressions for each of the following

\begin{enumerate}[label= (\alph*)]
  \item The number of strings of 7 lower case letters (a-z) that do not contain
    any letter twice or more.

  \item The number of binary strings of length 50 that contain at most three 1s.

  \item The number of ternary strings of length 10 (strings of 0s, 1s and 2s)
    containing one 1 and exactly four 2s.
\end{enumerate}

\section*{Question 4}

A small school with 14 students has a basketball team with 5 players, a chess
team with 4 players, a netball team with 7 players, and a soccer team with 11
players.

\begin{itemize}
  \item Each student is on at least one of these teams and no student is on all
    four teams.
  \item Only one student, Hawa, is on three of the teams; she plays chess,
    netball and soccer.
  \item There is exactly 1 student who plays basketball and chess.
  \item There is exactly 1 student who plays basketball and netball.
  \item Hawa is the only student who plays chess and netball.
  \item There are exactly 3 students (including Hawa) who play chess and soccer.
  \item There are exactly 5 students (including Hawa) who play netball and
    soccer.
\end{itemize}

How many students play basketball and soccer?

\end{document}
