\documentclass[11pt]{article}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{booktabs}

\begin{document}
\title{MAT1830 --- Assignment 8}
\author{Dylan Pinn --- 24160547}
\maketitle

\section*{Question 1}

One side of a 6-sided die is marked ``0'', two sides are marked ``2'', and three
sides are marked ``3''. Each side is equally likely to occur when the die is
rolled. The die is rolled twice and the results are recorded.

\noindent
Let $A$ be the event that the first roll is 0. \\
Let $B$ be the event that the second roll is 3. \\
Let $C$ be the event that the sum of the two rolls is 5.

\begin{enumerate}[label= (\alph*)]
  \item Find $\Pr(A)$, $\Pr(B)$, and $\Pr(C)$.

    \[ \Pr(A) = \frac{1}{6} \]
    \[ \Pr(B) = \frac{3}{6} = \frac{1}{2} \]
    \[ \Pr(C) = \frac{12}{36} = \frac{1}{3} \]

  \item Find $\Pr(A \cap B)$, $\Pr(A \cap C)$, and $\Pr(B \cap C)$.

    \[ \Pr(A \cap B) = \frac{3}{36} = \frac{1}{12} \]
    \[ \Pr(A \cap C) = 0 \]
    \[ \Pr(B \cap C) = \frac{6}{36} = \frac{1}{6} \]

  \item Are $A$ and $C$ independent events? Are $B$ and $C$ independent events?

    \[ \Pr(A \cap C) = \Pr(A)\Pr(C) \]
    \[ 0 = \frac{1}{6} \times \frac{1}{3} \]
    \[ 0 \not = \frac{1}{18} \]

    As these are not equal the events are not independent.

    \[ \Pr(B \cap C) = \Pr(B)\Pr(C) \]
    \[ \frac{6}{36} = \frac{1}{2} \times \frac{1}{3} \]
    \[ \frac{1}{6} = \frac{1}{6} \]

    As these are equal the events are independent.

  \item Find $\Pr(A \cup C)$ and $\Pr(B \cup C)$.

    \begin{align*}
      \Pr(A \cup C) &= \Pr(A) + \Pr(C) - \Pr(A \cap C) \\
      &= \frac{1}{6} + \frac{1}{3} - 0 \\
      &= \frac{3}{6} \\
      &= \frac{1}{2}
    \end{align*}

    \begin{align*}
      \Pr(B \cup C) &= \Pr(B) + \Pr(C) - \Pr(B \cap C) \\
      &= \frac{1}{2} + \frac{1}{3} - \frac{1}{6} \\
      &= \frac{4}{6} \\
      &= \frac{2}{3}
    \end{align*}

  \item Find $\Pr(B \mid B \cup C)$.

    \begin{align*}
      \Pr(B \mid B \cup C) &= \frac{\Pr(B \cap (B \cup C))}{\Pr(B \cup C)} \\
      &= \frac{\Pr(B)}{\frac{2}{3}} \\
      &= \frac{\frac{1}{2}}{\frac{2}{3}} \\
      &= \frac{3}{4}
    \end{align*}
\end{enumerate}

\break{}
\section*{Question 2}

Blofeld captures James Bond and places him in a pit with 100 deadly scorpions,
20 of which have been genetically engineered for extra deadliness. The normal
scorpions' bites are fatal $60\%$ of the time and the genetically engineered
scorpions' bites are fatal $90\%$ of the time. Bond escapes the pit, but is
bitten once by one of the scorpions. Given that Bond survives, what is the
probability that the scorpion that bit him was genetically engineered?

\bigskip
\noindent
Let $A$ be the event that Bond is bitten by a genetically engineered scorpion.
\\
Let $B$ be the event that Bond survives.

\begin{align*}
  \Pr(A) &= \frac{20}{100} = \frac{2}{10} \\
  \Pr(B \mid A) &= \frac{9}{10} \\
  \Pr(B \mid \bar A) &= \frac{6}{10} \\
  \Pr(\bar A) &= \frac{80}{100} = \frac{8}{10} \\
  \Pr(A \mid B) &= \frac{\Pr(B \mid A) \Pr(A)}{\Pr(B \mid A)\Pr(A) + \Pr(B \mid
  \bar A) \Pr(\bar A)} \\
  &= \frac{\frac{9}{10} \times \frac{2}{10}}{\frac{6}{10} \times \frac{2}{10} +
  \frac{6}{10} \times \frac{8}{10}} \\
  &= \frac{\frac{18}{100}}{\frac{12}{100}+\frac{48}{100}} \\
  &= \frac{\frac{18}{100}}{\frac{60}{100}} \\
  &= \frac{3}{10}
\end{align*}

\break{}
\section*{Question 3}

A word is chosen uniformly at random from the set

\[ \{ \text{there, was, a, wall, it, did, not, look, important} \}\]

\noindent
Let $X$ be the number of times the letter `t' occurs in the chosen word. Write
down the probability distribution of $X$.

\begin{center}
  \begin{tabular}{c c c c}
    \toprule
    $x$ & 0 & 1 & 2 \\
    $\Pr(X=x)$ & $\frac{5}{9}$ & $\frac{3}{9}$ & $\frac{1}{9}$ \\
    \bottomrule
  \end{tabular}
\end{center}

\end{document}
